---
title: 'Penguin Plots: Practice Penguins'
author: "Jean Miller"
date: "2023-06-12"
output:
  html_document: default
  pdf_document: default

---

## Setting up my environment
Notes: setting up my R environment by loading the 'tidyverse' and 'palmer penguins' packages

```{r loading packages}

library(tidyverse)
library(palmerpenguins)

```
## Visualizations

Here we will go through a series of visualizations

### Flipper and body mass with color distinction for species

Here we plot flipper length and body mass with color distinction for species.

```{r color distinction for species, message=FALSE, warning=FALSE}
ggplot(data = penguins) +
  geom_point(mapping = aes(x=flipper_length_mm, y = body_mass_g, color = species)) +
  labs(title = "Palmer Penguins: Body Mass vs. Flipper Length", subtitle = "Sample of Three Penguins") +
  labs (x = "Flipper Length (mm)", y = "Body Mass (g)")

```

### Flipper and body mass faceted

Here, we plot flipper length and body mass to look at the breakdown by species and sex.

```{r faceted visual, message=FALSE, warning=FALSE}
ggplot(data = penguins) +
         geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, color = species, shape = species)) +
         facet_wrap(~sex)

```

